### 2020-01-10 paper/paper.tex
Discussion Notes

>>>>

Chosing interpolations
monotonic vs. smooth (univariate spline stuff)

perfect degenercy between definition of "Centroid of line" and "wavelength solution"
cross correlation calls center of line something slightly different than what's happening when lines are being fit
may lead to systematic differences
in principle it would be preferable for the calibration source to look like a star
